Informing policy via dynamic models: Cholera in Haiti

### 2024-02-29 ms.Rnw
Edits related to name-ref of supplement files

\new{Confidence intervals for model parameters are given in supplement~S8.} %TODO: nameref this

@@

The starting value for each element of the latent state vector $\bm{X}(0)$ are set to zero except for $I_{u0}(0) = y_u^*(0)/\reportRate$ and $R_{u0}(0) = \mathrm{Pop}_u - I_{u0}(0)$, where $y_u^*(0)$ is the reported number of cholera cases in department $u$ at time $t = 0$.
Reported cases are described using a log-normal distribution, with the log-scale mean equal to the reporting rate $\reportRate$ times the number of newly infected individuals.
See the section describing how Model~2 is fit to data and Sec.~S3.2 of the supplement for more details.

@@

\begin{table}[!h]
\centering
\caption{\label{tab:likes}{\bf AIC values for Models~1--3 and their benchmarks.}}
\begin{tabular}{|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3}
\\
\hline
\hline
\multirow{2}{*}{Log-likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  $\Sexpr{myround(mod3_ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(unname(lee20_replication['leeFit_ll']), 1)}$) &
  ($\Sexpr{myround(lee3_results[["all_ll_eval"]], 1)}$)\footnotemark[2]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ &
  $\Sexpr{as.character(mod2_n_params)}$ &
  $\Sexpr{as.character(mod3_n_params)}$ \\
 Fit Parameters &
 (\Sexpr{as.character(mod1_lee_n_params)}) &
 ($\Sexpr{as.character(unname(lee20_replication['leeFit_n_params']))}$) &
 ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ &
  $\Sexpr{myround(mod2_aic, 1)}$ &
  $\Sexpr{myround(mod3_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(mod2_lee_aic, 1)}$) &
  ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[2]
\\
\hline
\thead{Benchmark \\ AIC} &
  $\Sexpr{myround(-2 * benchmarks$m1 + 2 * 4, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m2 + 2 * 40, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m3 + 2 * 40, 1)}$
\\
\hline
\end{tabular}
\begin{flushleft}
Values in parentheses are corresponding values \new{obtained} using \new{the models of \cite{lee20}} \old{Lee et al.~[4] parameter estimates}.  \textsuperscript{1}The reported likelihood is an upper bound of the likelihood of the \old{Lee et al.~[4]} model \new{in \cite{lee20}}. \old{Lee et al.~[4] fit} \textsuperscript{2}\new{In \cite{lee20},} Model~3 \new{was fit} to a subset of the data (March 2014 onward, excluding data from Ouest in 2015-2016).
On this subset, their model has a likelihood of $\Sexpr{myround(lee3_results$sub_ll_eval, 1)}$.
On this same subset, our model has a likelihood of $\Sexpr{myround(mod3_eval_res$subset_ll['est'], 1)}$.
Details of estimating the likelihood of the \old{Lee et al.~[4]} models \new{used in \cite{lee20} are} \old{is} provided in \nameref{S_lee20}
\old{See Sec.~S6 of the supplement material for more details on estimating the likelihood of the Lee et al.~[4] models.}
\end{flushleft}
\end{table}

@@

>>>>

\new{Confidence intervals for model parameters are given in the supplement (\nameref{S_CI}).}

@@

The starting value for each element of the latent state vector $\bm{X}(0)$ are set to zero except for $I_{u0}(0) = y_u^*(0)/\reportRate$ and $R_{u0}(0) = \mathrm{Pop}_u - I_{u0}(0)$, where $y_u^*(0)$ is the reported number of cholera cases in department $u$ at time $t = 0$.
Reported cases are described using a log-normal distribution, with the log-scale mean equal to the reporting rate $\reportRate$ times the number of newly infected individuals.
\old{See the section describing how Model~2 is fit to data and Sec.~S3.2 of the supplement for more details.}
\new{See the supplement material on model initializations for more details (\nameref{S_init})}

@@

\begin{table}[!h]
\centering
\caption{\label{tab:likes}{\bf AIC values for Models~1--3 and their benchmarks.}}
\begin{tabular}{|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3}
\\
\hline
\hline
\multirow{2}{*}{Log-likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  $\Sexpr{myround(mod3_ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(unname(lee20_replication['leeFit_ll']), 1)}$) &
  ($\Sexpr{myround(lee3_results[["all_ll_eval"]], 1)}$)\footnotemark[2]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ &
  $\Sexpr{as.character(mod2_n_params)}$ &
  $\Sexpr{as.character(mod3_n_params)}$ \\
 Fit Parameters &
 (\Sexpr{as.character(mod1_lee_n_params)}) &
 ($\Sexpr{as.character(unname(lee20_replication['leeFit_n_params']))}$) &
 ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ &
  $\Sexpr{myround(mod2_aic, 1)}$ &
  $\Sexpr{myround(mod3_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(mod2_lee_aic, 1)}$) &
  ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[2]
\\
\hline
\thead{Benchmark \\ AIC} &
  $\Sexpr{myround(-2 * benchmarks$m1 + 2 * 4, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m2 + 2 * 40, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m3 + 2 * 40, 1)}$
\\
\hline
\end{tabular}
\begin{flushleft}
Values in parentheses are corresponding values \new{obtained} using \new{the models of \cite{lee20}} \old{Lee et al.~[4] parameter estimates}.  \textsuperscript{1}The reported likelihood is an upper bound of the likelihood of the \old{Lee et al.~[4]} model \new{in \cite{lee20}}. \old{Lee et al.~[4] fit} \textsuperscript{2}\new{In \cite{lee20},} Model~3 \new{was fit} to a subset of the data (March 2014 onward, excluding data from Ouest in 2015-2016).
On this subset, their model has a likelihood of $\Sexpr{myround(lee3_results$sub_ll_eval, 1)}$.
On this same subset, our model has a likelihood of $\Sexpr{myround(mod3_eval_res$subset_ll['est'], 1)}$.
Details of estimating the likelihood of the \old{Lee et al.~[4]} models \new{used in \cite{lee20} are} \old{is} provided in \new{the supplement} (\nameref{S_lee20}).
\old{See Sec.~S6 of the supplement material for more details on estimating the likelihood of the Lee et al.~[4] models.}
\end{flushleft}
\end{table}

@@

\paragraph*{S7 Text}
\label{S_CI}
{\bf Confidence Intervals} Tables and figures describing 95\% confidence intervals for estimated parameters.
